<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{A package to facilitate the production of heatmaps}
-->

heatmapHIV: A package to facilitate the production of heatmaps
=================================================================

# Introduction

This short vignette will show how to use the `heatmapHIV` package.

```{r loadLibrary}
suppressMessages(library(heatmapHIV))
```

The main function is named `heatmapHIV` and will produce an heatmap using the
following files as input:

* A RPKM or raw data matrix in tsv format.
* A list of gene in csv format (one gene by line).

We need to give the function the path to both filename.

For this demo, we will use toy examples available with this package:

```{r loadToyExamples}
rpkm <- get_toy_rpkm()
gene_list <- get_toy_gene_list()
rpkm
gene_list
```

Once we have the path to the file, producing an heatmap is very simple:

```{r produceHeatmap}
heatmapHIV(rpkm, gene_list)
```

By default, the sequences will be clustered on columns only. It is also
possible to use the `filter` parameter to sort the rows based on the mean
RPKM of a subset of columns. The `filter` param is a character string that
that is found in the names of the columns we wish to use to sort the rows.

For instance, if we wish to order the matrix using the columns that contains
the pattern `Exp`:

```{r showFilter}
heatmapHIV(rpkm, gene_list, filter = "Exp")
```

Finally, the final `matrix` used to produce the heatmap is silently returned:

```{r silentMatrix}
current_matrix <- heatmapHIV(rpkm, gene_list)
class(current_matrix)
dim(current_matrix)
```
